<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-10-25 MainAnalysis.Rmd
Got plot_conctime working

```{r, run_invivoPKfit, eval = TRUE}

THIS.DATE <- "102422"

@@

# data <- read.csv("inst/ext/cvt_query_for_john_27may2021_v2.csv")
# data <- read.csv("inst/ext/cvtdb_invivopkfit_02242022.csv")
# data <- read.csv("inst/ext/cvtdb_invivopkfit_04142022.csv")
data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022.csv")

@@

data <- data %>%
  filter(analyte_name_original != "Methemoglobin") %>%
  filter(analyte_name_original != "N-desmethyltamoxifen")

@@

### fix compound names
data$analyte_name_original[data$analyte_name_original == "Methyleugonal "] <- "Methyleugonal"
data$analyte_name_original[data$analyte_name_original == "benzo[a]pyrene"] <- "benzo(a)pyrene"
data$analyte_name_original[data$analyte_name_original == "2,4-D"] <- "2,4-Dichlorophenoxyacetic acid"
data$analyte_name_original[data$analyte_name_original == "Diclofenac"] <- "Hexobarbital"
data$analyte_name_original[data$analyte_name_original == "Pentadecafluorooctanoic acid"] <- "Perfluorooctanoic acid"
data$analyte_name_original[data$analyte_name_original == "3−hydroxybenzo[a]pyrene"] <- "3−hydroxybenzo(a)pyrene"

### make fk_reference_document equal fk_extraction document if fk_reference_document is NULL
data$fk_reference_document_id[data$fk_reference_document_id == "NULL"] <- data$fk_extraction_document_id[data$fk_reference_document_id == "NULL"]

### this is basically my debug line,
# where I can focus on one problematic compound 
# and see what's going wrong
# data <- data %>% filter(dsstox_casrn == "68291-97-4" | dsstox_casrn == "82626-48-0")
# data <- data %>% filter(dsstox_casrn == "123-91-1")

### do 1-Compartment fit
system.time(PK.fit.table.1comp <- fit_all(
  data.set = data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))

### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(
  data.set = data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))

### do flat fit
system.time(PK.fit.table.flat <- fit_all(
  data.set = data,
  model = "flat",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))

>>>>

```{r, load_cvt, eval = TRUE}

@@

# data <- read.csv("inst/ext/cvt_query_for_john_27may2021_v2.csv")
# data <- read.csv("inst/ext/cvtdb_invivopkfit_02242022.csv")
# data <- read.csv("inst/ext/cvtdb_invivopkfit_04142022.csv")
cvt.data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022.csv")

@@

cvt.data <- cvt.data %>%
  filter(analyte_name_original != "Methemoglobin") %>%
  filter(analyte_name_original != "N-desmethyltamoxifen")

@@

### fix compound names
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Methyleugonal "] <- "Methyleugonal"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "benzo[a]pyrene"] <- "benzo(a)pyrene"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "2,4-D"] <- "2,4-Dichlorophenoxyacetic acid"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Diclofenac"] <- "Hexobarbital"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Pentadecafluorooctanoic acid"] <- "Perfluorooctanoic acid"
cvt.data$analyte_name_original[cvt.data$analyte_name_original == "3−hydroxybenzo[a]pyrene"] <- "3−hydroxybenzo(a)pyrene"

### make fk_reference_document equal fk_extraction document if fk_reference_document is NULL
cvt.data$fk_reference_document_id[cvt.data$fk_reference_document_id == "NULL"] <- 
  cvt.data$fk_extraction_document_id[cvt.data$fk_reference_document_id == "NULL"]

### this is basically my debug line,
# where I can focus on one problematic compound 
# and see what's going wrong
# data <- data %>% filter(dsstox_casrn == "68291-97-4" | dsstox_casrn == "82626-48-0")
# data <- data %>% filter(dsstox_casrn == "123-91-1")
```

Calculate a limit of quantification (90% of lowest observation)
```{r, calc_loq, eval = TRUE}
source.col <- "fk_study_id"
cas.col <- "dsstox_casrn"
media.col <- "conc_medium_normalized"
value.col <- "conc"
for (this.study in unique(cvt.data[,source.col]))
{
  this.subset1 <- subset(cvt.data,cvt.data[,source.col]==this.study)
  for (this.chem in unique(this.subset1[,cas.col]))
  {
    this.subset2 <- subset(this.subset1,this.subset1[,cas.col]==this.chem)
    for (this.media in unique(this.subset2[,media.col]))
    {
      this.subset3 <- subset(this.subset2,this.subset2[media.col]==this.media & 
        !is.na(this.subset2[,value.col]))
      this.subset3 <- subset(this.subset3,this.subset3[,value.col]>0)
      this.loq <- suppressWarnings(min(this.subset3[,value.col], na.rm=TRUE))
      this.loq <- this.loq*0.9
      cvt.data[
        cvt.data[,source.col]==this.study & 
        cvt.data[,cas.col]==this.chem & 
        cvt.data[,media.col]==this.media,"calc_loq"] <- this.loq
    }
  }
}
cvt.data <- subset(cvt.data,!is.infinite(calc_loq))

```{r, run_invivoPKfit_1comp, eval = TRUE}
THIS.DATE <- "102422"
### do 1-Compartment fit
system.time(PK.fit.table.1comp <- fit_all(
  data.set = cvt.data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))
```

```{r, plot_1comp, eval=TRUE}
plot_conctime(PK.fit.table.1comp[[1]],cvt.data,"1compartment")
head(subset(PK.fit.table.1comp[[1]],Vdist>10000&!is.infinite(AIC)&param.value.type=="Fitted geometric mean"))
```

```{r, run_invivoPKfit_2comp, eval = TRUE}
### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(
  data.set = cvt.data,
  model = "2compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))
```

```{r, run_invivoPKfit_flat, eval = TRUE}
### do flat fit
system.time(PK.fit.table.flat <- fit_all(
  data.set = cvt.data,
  model = "flat",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA
))
